---
title: "Data Analysis"
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| label: init

options(scipen=999)

library(tidyverse)
library(readr)
library(janitor)
library(lubridate)
library(stringi)
library(rlang)
library(plotly)
library(htmlwidgets)

source("loader.R")
source("chipHandler.R")
source("plots/plot_topViews.R")
source("plots/plot_topLikes.R")
source("plots/plot_likeViewRatio.R")
source("plots/plot_perChipUsage.R")

```

# The Top

The top 20 most viewed videos are:
```{r}
#| label: topViews
plot_topViews
```
And the top 20 most liked are:
```{r}
#| label: topLikes
plot_topLikes
```
Obviously the most viewed videos will be the most liked.

If we plot by the like / view ratio:
```{r}
#| label: topLikeViewRatio
plot_likeViewRatio
```
Kinda sad that the highest ratio comes from the lowest stats.<br>
I guess it shows who has the most loyal audience?

# The Chips
**!!!**
```{r}
#| label: perChipUsage
plot_perChip
```

The ESFM and Virtual Boy peaks around 2024 correspond to the ESFM and VB demo song contests.<br>
The most used chip is (as expected) the YM2612. Of course it is, it's the default!
